Towards Correct Legion

### 2017-08-24 correctnesshpc/paper.tex
Small changes

One of the core notions of Legion is the notion of region relations. These
describe how regions are related, either by being disjoint, or by being
subregions of one another. See Figure~\ref{regionrel} for the syntax.

@@

TODO: Noah, if you want to put a rough description of your preservation proof 
here feel free. Your type inference isn't loading for me.

>>>>

One of the core notions of Legion is the notion of region relations. These
describe how regions are related, either by being disjoint, or by being
subregions of one another. See Figure~\ref{regionrel} for the syntax. Another
important construction are mappers, \texttt{M}, which map logical regions
\texttt{r} with a set of physical locations. We include some definitions as
well, notably the notion that a mapping respects (\texttt{resp}) a set of
region requirements iff for every subregion relation and disjoint relation, the
mapping to sets of physical locations follows the corresponding set relation.

@@

TODO: Noah, if you want to put any other proof stuff here feel free.
